Analysis of 2005-2015 Earthquake Sequence in Northern Iran Using Visibility Graph Approach

### 2016-06-01 abstract.tex
Added shima's comments.

\begin{abstract}
The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method. According to the seismicity, in this study the northern Iran is divided into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.  The aftershocks and foreshocks are removed from the catalog and the magnitude time series are generated for each tectonic seismic zone. Using declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e. $< T_c >$, $k-M$ slope) of network and  dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Cumulating the results of this study into two similar previous studies, improves the linear correlation coefficient factor and empower the idea of universal relationship between $b-value$ and $k-M$ slope. The behavior of  the VG's properties are similar to previous studies and could be considered an alternative method to analyze the earthquake sequence. 
\end{abstract}

>>>>

\begin{abstract}
The seismicity of northern Iran between 2005 and 2015 is investigated by means of visibility graph (VG) method. In this study the northern Iran is divided into three tectonic seismic regions: Azerbaijan, Alborz, and Kopeh Dagh.  The aftershocks and foreshocks are removed from the catalog and the magnitude time series are generated for each tectonic seismic zone. Using declustered catalog, we studied the VG properties of the magnitude time series. The results show a relationship between the $k-M$ slope and the $b-value$ of the Gutenberg-Richter law. Topological properties (i.e. $< T_c >$, $k-M$ slope) of network and  dynamic properties of magnitude time series (i.e. $b-value$) significantly decrease before large earthquakes. Combining  the results of this study with two similar previous studies, improves the linear correlation coefficient factor and empower the idea of universal relationship between $b-value$ and $k-M$ slope. The behavior of  the VG's properties are similar to previous studies and could be considered an alternative method for analyzing the earthquake sequence. 
\end{abstract}

### 2016-06-01 introduction.tex
Added shima's comments.

\section{Introduction}
\noindent
\citet{Lacasa2008} presented a simple and fast computational method; known as visibility algorithm, to convert the time series into the graphs. Basically the visibility graph presents the connection between nodes in the network. In each time series two characteristics are attributed to each incidents, including the time and the value of the incident. Two events are connected to each other, or visible to each other, if there is not any other event to interrupt their linear connection. In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:

@@

\noindent
where, $y$ is the value of the event and $t$ is the time of the event. $k$ is the index of any event between event $i$ and event $j$.

\noindent
The visibility graph that is generated from the time series holds the following conditions, 1) each event is visible to the events at the right and left side (if there is any) of the event  (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  3) Rescaling or translation of the time series are not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}.

\noindent
The analysis of seismicity sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series. \citet{Telesca2012} studied the seismic sequence of Italy between 2005 and 2010 through using the visibility graph method. Using different threshold magnitude, and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and independent of the threshold magnitude. In other study, \citet{Telesca2013} studied the Seismicity of the Mexican subduction zone through visibility graph approach. They extracted the characteristics of the visibility graph for five different tectonic seismic regions.  According to their study visibility graph could identify one of the regions that has a different seismicity characteristics, which is because of different tectonic processes that governs the area. The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line of Magnitude  of each event $(M)$ and its connectivity degree $k$) is investigated in their study. In a similar study \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph. They classified seismic catalog into shallow and deep earthquakes and extract the visibility graph characteristics for each class. According to their study there is close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph. High linear correlation coefficient of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.  \citet{Telesca2016} , used the $ <T_C>$, as the parameter window mean interval connectivity time ,  that indicates the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequences in the Kachchh region of western India. They found that the $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary; also $<T_C>$ significantly decrees before the largest shock of the catalog. Analyzing Gutenberg-Richter values of  magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series using the features of networks. \\

\noindent
In this study we used visibility graph analysis to study the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.  Recently, northern Iran has been studied in detail from different seismological points of view. \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran. The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region. \\

\noindent
Northern Iran has an elaborate seismic history.  Having considerable number of earthquake and also being in different seismic tectonic zone, northern Iran is a good platform to analysis the visibility graph method's capabilities for studying the magnitude time series. In this study we present the relationship between $K-M$ slope and the $b-value$ in three different tectonic seismic region. We also investigate the variation of $<T_C>$ value through time.

>>>>

\section{Introduction}
\noindent
\citet{Lacasa2008} introduced a simple and fast computational method; known as visibility algorithm, to convert time series into graphs. Basically the visibility graph presents the connection between nodes in the network. For any time series, two characteristics are attributed to each incidents: ocurrance time and value of the incident. Two events are in connection or visible to each other, if no other event interrupts their linear connection. In mathematical form, event $i$ and event $j$ are visible to each other if the following equation fulfills:

@@

\noindent
where, $y$ is the value and $t$ is the time of the event. $k$ is the index of any event occurring between event $i$ and event $j$. The visibility graph generated from the time series holds the following conditions, 1) each event is visible to the first event at the right and left side (if there is any) of the event  (Connectivity), 2) The algorithm is developed without defining a direction for the links (Undirected),  3) Rescaling or translation of a time series is not changing the resulted visibility graph (Invariant under affine transformations of  the series data)\citep{Lacasa2008}. This concept has applications ranging in various fields including geophysical studies.

\noindent
The analysis of seismic sequence through visibility graph for various tectonic seismic regions, revealed an alternative approach to study the magnitude time series. \citet{Telesca2012} studied the seismic sequence of Italy between year 2005 and 2010 through using the visibility graph method. Applying different threshold magnitude and observing the collapsing effect of all the distribution degrees, they argued that in analyzing the magnitude time series, VG seems to depend only on the values of the magnitude and independent of the threshold magnitude. In another research, \citet{Telesca2013} studied the Seismicity of the Mexican subduction zone through visibility graph approach. They extracted the characteristics of the visibility graph for five different tectonic seismic regions.  According to their study visibility graph could identify one of the regions that has a different seismicity characteristics, which is because of different tectonic processes that governs the area. The relationship between Gutenberg-Richter parameters and $k-M$ slope (The slope of regression line of Magnitude  of each event $(M)$ and its connectivity degree $(k)$) is investigated in their study. In a similar article \citet{Telesca2014}, studied the seismicity of 2002-2011 Pannonian seismicity using the visibility graph. They classified seismic catalog into shallow and deep earthquakes and extract the visibility graph characteristics for each class. According to their study there is a close relationship between Gutenberg-Richter $b-value$ and $k-M$ slope of the visibility graph. High linear correlation coefficient value (close to 1)of $b-value$ and $k-M$ slope suggests the universal character of the relationship between these parameters \citep{Telesca2014}.  \citet{Telesca2016} , used the $ <T_C>$, as the parameter window mean interval connectivity time ,  that indicates the mean linkage time between earthquakes, to study the 2003-2012 earthquake sequences in the Kachchh region of western India. They found that the $<T_C>$ changes through time, indicating that the topological properties of the earthquake network are not stationary; also $<T_C>$ significantly decrees before the largest shock of the catalog. Analyzing Gutenberg-Richter values of  magnitude time series of an earthquake sequence revealed more opportunities to study the magnitude time series using the features of networks. \\

\noindent
In this study we used visibility graph analysis to investigate the earthquake sequence of northern Iran. We divided northern Iran into three tectonic seismic regions including Azerbaijan, Alborz, and Kopeh Dagh.  Recently, northern Iran has been studied in detail from different seismological points of view. \citet{Nemati2015} studied the most recent 200 years' seismicity in northern Iran. The frequency of shocks vary widely from one main shock per 6 years (0.17 event/ year) for the Azerbaijan region to 13 earthquakes per 4 years for the Kopeh-Dagh (3.25 event/year) region. \\

\noindent
Northern Iran has an elaborate seismic history.  Having considerable number of earthquakes and also being in different tectonic seismic zone, northern Iran is a good platform to analyze the visibility graph method's capabilities for studying the magnitude time series. In this study we present the relationship between $k-M$ slope and the $b-value$ in three different tectonic seismic regions. We also investigate the variation of $<T_C>$ value through time.

### 2016-06-01 results.tex
Added shima's comments.

\section{Results}
\noindent
We generated the visibility graph characteristics for three tectonic seismic regions in northern Iran for the period from 2005 to 2015. Number of earthquake in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}.

@@

\noindent
We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding window in time. The $b-value$ is generated through the maximum likelihood estimation \citep{Aki1965}.

@@

 \noindent
 where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone. Number of sequences and threshold magnitude are considerably different for all tectonic seismic zones. \citet{Telesca2013} studied the effect of number of earthquake in catalog on the $k-M$ slop. Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.  According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly picked 200 sequence from the catalogs with various sequence size. The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the whole catalog. For each randomly picked magnitude time series we estimated the $Mc$ and calculated the $k-M$ and $b-value$. Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables. Although changing number of events and the threshold magnitude are slightly change the results, they are fairly well clustered for each tectonic seismic region.

@@

 \noindent
The $k-M$ slope shows the maximum coefficient of variation. We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slop can better represent the dynamic characteristics of the magnitude-time series.

 \noindent
 Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic zones in Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. Adding the results of this study into two previous similar studies' results, improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:regression}
\end{figure}

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 40 events as a window length with shift of one event between two successive window. There is a very good similarity between the $K-M$ slope and $b-value$ in all tectonic seismic regions. In general, In all regions the $b-value$ and $K-M$ slope considerably drop before big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

\noindent
\citet{Telesca2016} observed the decreasing of the $<Tc>$ before large earthquake of Western India earthquake sequence. Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area. The decreasing of the $<Tc>$ for large earthquakes have been shown in the figure. \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude. The fluctuation of magnitude time series' topology properties (e.g. the $k-M$ slope and $<Tc>$) could be affected by the window size. Sharp changes in the VG parameters happens through small windows. Using higher number of samples in the window will reduce the temporal effects of small or moderate earthquakes and highlight the effects of big earthquakes, even though the behavior of the parameters in time and also before big earthquake are similar \citep{Telesca2016}. In general, more number of samples in a window smooth the results and highlight the effect of events with big magnitudes.

>>>>

\section{Results}
\noindent
We generated the visibility graph parameters for three tectonic seismic regions in northern Iran for the period from 2005 to 2015. Number of earthquakes in each catalog after declustering and the seismicity parameters are presented in Table.~\ref{tab:b_k_m_param}.

@@

\noindent
We compared the $k-M$ slope with the $b-value$ of the Gutenberg-Richter law in the whole catalog and also in the sliding windows in time. The $b-value$ is generated through the maximum likelihood estimation \citep{Aki1965}.

@@

 \noindent
 where $\overline{M}$ is the average magnitude and $M_{min}$ is the minimum magnitude in the sample, which in this case is the completeness magnitude for each tectonic seismic zone. Number of sequences and threshold magnitudes are considerably different for all tectonic seismic zones. \citet{Telesca2013} studied the effect of the number of earthquakes in catalog on the $k-M$ slope. Comparing the result of Guerrero region with reduced random sequence, \citet{Telesca2013} found that the number of sequence doesn't affect the $k-M$ slope.  According to \citet{Telesca2012}, the threshold magnitude has a minor effect in the VG parameters. In order to analyze the sensitivity of the catalogs to the number of events and the threshold magnitude we randomly pick 200 sequence from the catalogs with various sequence size. The minimum size of random windows are 150 events (note that the number of events in each catalog, before removing the events with magnitude less than completeness magnitude, are 271, 1262, and 399 for Azerbaijan, Alborz, and Kopek Dagh regions, respectively) and the maximum size is the size of the whole catalog. For each randomly picked magnitude time series we estimate the $Mc$ and calculated the $k-M$ and $b-value$. Fig.~\ref{fig:random} shows the relationship between $k-M$ slope and $b-value$ of the randomly selected data and statistical parameters for variables. Although changing the number of events and the threshold magnitude are slightly changes the results, they are fairly well clustered for each tectonic seismic region.

@@

 \noindent
The $k-M$ slope shows higher coefficient of variation. We may argue that the $k-M$ slope is much dependent to the window size and threshold magnitude than $a-$ and $b-value$, which suggest the idea that $k-M$ slope can better represent the dynamic characteristics of the magnitude-time series.

 \noindent
 Fig.~\ref{fig:regression} shows the relationship between the $k-M$ slope for three tectonic seismic regions in north of Iran and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. Adding the results of the current study into the results of two previous similar studies improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} concluded.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $k-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:regression}
\end{figure}

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 20 events as a window length with shift of one event between two successive windows. There is a very good similarity between the $k-M$ slope and $b-value$ in all tectonic seismic regions. In general, In all regions the $b-value$ and $K-M$ slope considerably drop before big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

\noindent
\citet{Telesca2016} observed the decreasing of the $<Tc>$ before large earthquake of Western India earthquake sequence. Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area. The decreasing of the $<Tc>$ for large earthquakes have been shown in the figure. \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude. The fluctuation of magnitude time series' topology properties (e.g. the $k-M$ slope and $<Tc>$) could be affected by the window size. Sharp changes in the VG parameters happens through small windows. Using higher number of samples in the window will reduce the temporal effects of small or moderate earthquakes and highlight the effects of big earthquakes, even though the behavior of the parameters in time and also before big earthquake are similar \citep{Telesca2016}. %In general, more number of samples in a window smooth the results and highlight the effect of events with big magnitudes.

### 2016-06-01 seismicity.tex
Added shima's comments.

\section{Tectonic seismic zones and seismicity parameters}
\noindent
Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes. These earthquakes are categorized in various tectonic seismic zones. Based on seismicity parameters different tectonic seismic devisions have been defined for Iran.  Some studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}. \citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran. Considering \citet{Mirzaei1998} devision, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz). Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.  Fig.~\ref{fig:study_region} shows the study region and tectonic seismic regions. \\

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure01.pdf} 
\caption{a) Map of Iran and surrounding countries. The study area is presented in gray box. b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
\label{fig:study_region}
\end{figure}

@@

\subsection{Magnitude Conversion}
\noindent
The catalog of recorded earthquake from 2005-2015 which is downloaded from IIEES is reported the earthquake based on different magnitude scale (reference). We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which is defined in \citet{Zare2014}. There also some of data which is recorded in $M_D$ (Duration magnitude). These data are reported by International Seismological Centre (ISC).  \citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes in $mb$, $M_D$, $M_L$ and $M_S$ scales to the $M_W$ scales using orthogonal regression procedure. They used data of earthquake that occurred in Turkey from different data centers including ISC. In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$. Although they defined the equation based on $4.5\leqslant M_W$, we extrapolate the equation for lower magnitude. We believe having those earthquakes, even with small error  in magnitude is important for estimating an accurate  Gutenberge-Richter values.

@@

\subsection{Catalog Completeness}
\noindent
Completeness of catalog is an important factor in studying the earthquake sequence.  In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000}. According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for picking the completeness magnitude for each catalog include, 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generate  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculate the goodness of fit for predicted and observed cumulative numbers for each magnitude bin. Higher \citep{Wiemer2000}. We increase the minimum magnitude and repeat the process. For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit.  \citet{Wiemer2000} assumed the threshold of goodness of fit as 90\% in order to completeness of the catalog, however,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} , shows the goodness of fit value for three tectonic seismic regions.

@@

\noindent
In this study we assumed the minimum magnitude for complete recording, $M_C$, are 2.9, 3.5, and 2.6 for Alborz, Azerbaijan, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for three regions. Earthquake with magnitude bigger than completeness magnitude are represented.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
\caption{Variation of moment magnitude of earthquake in 2005-2015 for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
\label{fig:mag-time}
\end{figure}

>>>>

\section{Tectonic seismic regions and seismicity parameters}
\noindent
Iran is situated over Himalayan-Alpide seismic belt, which has frequently experienced strong shaking induced by earthquakes. These earthquakes are categorized in various tectonic seismic zones. Based on seismicity parameters different tectonic seismic devisions have been defined for Iran.  Some studies defined more detailed division \citep{Nowroozi1976, Tavakoli1999}, and some of them defined one simplified province \citep{Stocklin1968, Takin1972, Berberian1976}. \citet{Mirzaei1998} divided Iran into five tectonic regions, including Azerbaijan-Alborz, Kopeh-Dagh, Zagros, Central-East Iran, and Makran. Considering \citet{Mirzaei1998} devision as a reference, \citet{Karimiparidari2013} divided the Azerbaijan-Alborz tectonic seismic region into two regions, which are Azerbaijan and Alborz Mountain Range (hereinafter, Alborz). Azerbaijan, Alborz and Kopeh-Dagh tectonic seismic regions encompass most of northern Iran.  Fig.~\ref{fig:study_region} shows the study area and tectonic seismic regions. \\

\begin{figure} [ht]
\centering
\includegraphics[scale=0.6]{figures/pdf/Figure01.pdf} 
\caption{a) Map of Iran and surrounding countries. The study area is situated in the gray box. b) The study area containing seismotectonic provinces after \citet{Mirzaei1998}, and location of big cities indicated with circles. Dashed line is the subdivision that is proposed by \citet{Karimiparidari2013}}
\label{fig:study_region}
\end{figure}

@@

\subsection{Magnitude Conversion}
\noindent
The catalog of recorded earthquakes from 2005-2015, which is downloaded from IIEES, reported the earthquakes based on different magnitude scale (reference). We converted the $M_L$, $M_S$, and $mb$ magnitudes through conversion relationships which are defined in \citet{Zare2014}. There are also some of data recorded in $M_D$ (Duration magnitude). These data are reported by International Seismological Centre (ISC).  \citet{Deniz2010} developed a set of empirical equations to convert earthquake magnitudes from $mb$, $M_D$, $M_L$ and $M_S$ scales to $M_W$ scales using orthogonal regression procedure. They used data of earthquake that occurred in Turkey from different data centers including ISC. In this study we use the conversion equation of \citet{Deniz2010} to convert the $M_D$ to $M_W$. Although \citet{Deniz2010} defined the equation based on $4.5\leqslant M_W$, we extrapolate the equation for lower magnitude. We believe having those earthquakes, even with small error  in magnitude is important for estimating accurate  Gutenberge-Richter values.

@@

\subsection{Catalog Completeness}
\noindent
Completeness of catalog is an important factor in studying the earthquake sequence.  In this study we used the Maximum curvature method (MAXC) \citep{Wiemer2000}. According to MAXC method, a complete catalog should follow the Gutenberg-Richter power law distribution of magnitude. The steps for picking the completeness magnitude for each catalog include, 1) Calculating the $a-$ and $b-$ value based on the minimum magnitude, 2) generating  synthetic events based on the achieved value that the cumulative number of events obey the power law distribution, 3) Calculating the goodness of fit for predicted and observed cumulative numbers for each magnitude bin \citep{Wiemer2000}. We increase the minimum magnitude and repeat the process. For each tectonic seismic region, we pick the magnitude corresponding to the highest goodness of fit.  \citet{Wiemer2000} assumed the threshold of goodness of fit as 90\% as a threshold to select completeness of the catalog, however,  not all frequency-magnitude distributions reach the 90\% mark. Fig.~\ref{fig:completeness} , shows the goodness of fit value for three tectonic seismic regions.

@@

\noindent
In this study we assumed the minimum magnitudes for complete recording, $M_C$, are 3.5, 2.9, and 2.6 for Azerbaijan, Alborz, and Kopeh Dagh, respectively. Fig.~\ref{fig:mag-time} shows the magnitude time series of the declustered data for three regions. Earthquakes with magnitude bigger than completeness magnitude are represented.

\begin{figure} [ht]
\centering
\includegraphics[scale=0.5]{figures/pdf/Figure04.pdf} 
\caption{Variation of moment magnitude of 2005-2015 earthquake for north Iran. (a) Azerbaijan b)Alborz c) Kopeh Dagh)}
\label{fig:mag-time}
\end{figure}
